Imperfect slope measurements drive overestimation in geometric cone model of waterbody depth

### 2021-11-11 README.Rmd
mint code doi

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246)

>>>>

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-10.5281/zenodo.5672711-blue.svg)](https://doi.org/10.5281/zenodo.5672711) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246)

### 2021-11-11 manuscript/manuscript.Rmd
mint code doi

Covariates used in random forest modeling (Table \ref{table1}, Equation 3, see Random Forests Model sub-section below) for waterbody elevation, area, island area, perimeter, shoreline development, watershed to waterbody area ratio, and hydrologic subbasin (i.e. HUC4s), were obtained from the LAGOS-US LOCUS database. One such measure, that of shoreline development, is a measure of waterbody perimeter shape defined as:

@@

All data used in the study is available at \citet{stachelekjemmaBathymetryData0002021}. All code for data processing, model fitting, and model evaluation is available at [Zenodo DOI].

>>>>

Covariates used in random forest modeling (Table \ref{table1}, Equation \ref{eq3}, see Random Forests Model sub-section below) for waterbody elevation, area, island area, perimeter, shoreline development, watershed to waterbody area ratio, and hydrologic subbasin (i.e. HUC4s), were obtained from the LAGOS-US LOCUS database. One such measure, that of shoreline development, is a measure of waterbody perimeter shape defined as:

@@

All data used in the study is available at \citet{stachelekjemmaBathymetryData0002021}. All code for data processing, model fitting, and model evaluation is available at \citet{jemstachelekContlimnoBathymetryAccepted2021}.
